---
title: "Estimation of COVID-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```


Load the time series data and covariates.

```{r}
path <- getwd()
setwd(paste0(path,"/dataset"))
time_series_data <- read.csv("new_time_series_data.csv")
Y = as.matrix(time_series_data[,-1])
design_matrix <- read.csv("new_design.csv")
X = as.matrix(design_matrix[,-c(1:2)])
```


```{r, cache=TRUE}
setwd(paste0(path,"/functions"))
source(file = "covid_curve.R")
library("compiler")

COVID19_curve = cmpfun(COVID19_curve)
# Execution
seed.no = 1 ; burn = 10000 ; nmc = 5000 ; thin = 10
varrho = 0
pro.var.theta.2 = 0.0002 ; pro.var.theta.3 = 0.05
mu = 0 ; rho.sq = 1

res_cov <- COVID19_curve(Y = Y, X = X, seed.no = seed.no, burn = burn, nmc = nmc, thin = thin, 
                 varrho = varrho, pro.var.theta.2 = pro.var.theta.2, pro.var.theta.3 = pro.var.theta.3, mu = mu, rho.sq = rho.sq) 
save(res_cov, file="result.RData")
```

```{r}
result = load("result.RData")
```

Draw the extrapolated infection trajectories and flat time points

```{r}
setwd(paste0(path,"/functions"))
source("visualizations_individual.R")
source("flat_time_point.R")
```

## US

Draw the figure for US:
```{r}
output <- visualizations_individual(38, res_cov, time_series_data)
output$figure
```

The epidemic size for the US:
```{r}
output$epidemic_size
```

The flat time points for the US ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```

## Russia

Draw the figure for Russia:
```{r}
output <- visualizations_individual(32, res_cov, time_series_data)
output$figure
```

The epidemic size for the Russia:
```{r}
output$epidemic_size
```

The flat time points for the Russia ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```

## United Kingdom

Draw the figure for United Kingdom:
```{r}
output <- visualizations_individual(40, res_cov, time_series_data)
output$figure
```

The epidemic size for the United Kingdom:
```{r}
output$epidemic_size
```

The flat time points for the United Kingdom ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```

## Brazil

Draw the figure for United Brazil:
```{r}
output <- visualizations_individual(4, res_cov, time_series_data)
output$figure
```

The epidemic size for the Brazil:
```{r}
output$epidemic_size
```

The flat time points for the Brazil ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```

## South Korea

Draw the figure for South Korea:
```{r}
output <- visualizations_individual(21, res_cov, time_series_data)
output$figure
```

The epidemic size for South Korea:
```{r}
output$epidemic_size
```

The flat time points for South Korea ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```


## Japan

Draw the figure for Japan:
```{r}
output <- visualizations_individual(20, res_cov, time_series_data)
output$figure
```

The epidemic size for Japan:
```{r}
output$epidemic_size
```

The flat time points for Japan ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```



## China

Draw the figure for China:
```{r}
output <- visualizations_individual(7, res_cov, time_series_data)
output$figure
```

The epidemic size for China:
```{r}
output$epidemic_size
```

The flat time points for China ($\epsilon=0.9,0.99,0.999,0.9999$):
```{r}
output$flat_time
```